---
title: "Zoning real yield data"
author: "B. Charnomordic"
date: "`r Sys.Date()`"
output:
    pdf_document:
    toc: yes
vignette: >
  %\VignetteIndexEntry{zoning field (yield) data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,echo=TRUE,message=FALSE, warning=FALSE}
  library(geozoning)
  library(ggplot2)

```
This vignette illustrates the zoning with correction procedure on real yield data. It uses the yield data available in the geozoning package, where coordinates are not normalized between 0 and 1. The field is rectangular.
A boundary is manually defined around the field.
Then the x coordinate is normalized between 0 and 1, and the y coordinate is normalized with the ratio used for x.

Exploratory loops for size 1 to 4 probability vectors (producing 2 to 5 labels maps) are run to rank the zonings, for each number of labels independently, according to their quality criterion.
Probability vectors corresponding to the best zonings for each number of labels are extracted from the loop results. Correction procedures are then run for each of these best zonings.
For readability, zones are reordered by increasing average value. An example of plot is given for the best 4-label zoning, to view zones and the distribution of values within zones.


```{r,echo=TRUE,message=FALSE, warning=FALSE}
# Import yield data
  data(yield)
```

```{r,echo=TRUE,message=FALSE, warning=FALSE}
  # draw manual boundary
  boundary0=list()
  boundary0$x=c(7723128,7723223,7723283,7723376,7723430,7723453,7723605,7723713,7723699,7723638,7723696,7723707,
                7723562,7723531,7723494,7723459,7723344,7723356,7723221,7723158,7723129)

  boundary0$y=c(3576538,3576438,3576432,3576396,3576386,3576388,3576776,3577000,3577054,3577104,3577175,3577202,
                3577389,3577388,3577455,3577445,3577211,3577151,3576860,3576697,3576547)

  boundary0$x[length(boundary0$x)]=boundary0$x[1]
  boundary0$y[length(boundary0$y)]=boundary0$y[1]
  
  boundary1<-cbind.data.frame(boundary0$x,boundary0$y)
  colnames(boundary1)<-c("x","y")
  
  # plot data
  ggplot(data=yield,aes(x=x,y=y,colour=Yield)) + geom_point() #+
    geom_line(data=boundary1, aes(x=x,y=y),col="red")
 
```

```{r,echo=TRUE,message=FALSE, warning=FALSE}
  #  x and y coordinates are normalized in genMap with (xmax-xmin) ratio

  # build map data based on yield data
  map=genMap(yield,seed=0,boundary=boundary0,disp=0,nPointsK=3000,krig=1)
  boundaryN=map$boundary
  dispZ(map$step,matVal=map$krigGrid,zonePolygone=NULL,boundary=map$boundary)
  

```
```{r,echo=TRUE,message=FALSE, warning=FALSE}	
# test zoning with one quantile (median value)
qProb=0.5
ZK = initialZoning(qProb,map)
K=ZK$resZ
Z=K$zonePolygone
dispZ(map$step,map$krigGrid,zonePolygone=Z,K=K,boundary=map$boundary,nbLvl=0,id=FALSE)
minSizeNG=0.001
minSize=0.012
#apply corrections and display detailed information at each step
criti= correctionTree(qProb=c(0.5),map,minSize=minSize,minSizeNG=minSizeNG,disp=1)
# search for best criterion at last level (once all corrections have been applied)
res=searchNODcrit1(qProb,criti)
b=res$ind[[1]][1]
K=criti$zk[[2]][[b]]
Z=K$zonePolygone
dispZ(map$step,map$krigGrid,zonePolygone=Z,K=K,boundary=map$boundary,nbLvl=0,id=FALSE)
#
#Run exploratory loops to find the best zonings for nL=2 to 5
#Set reasonable values for minimum size of zones and size threshold for not trying to grow zones (just remove them)
minSizeNG=1e-2
minSize=2e-2
#
ro1=loopQ1(map,disp=0,step=0.15,minSize=minSize,minSizeNG=minSizeNG)
ro2=loopQ2(map,disp=0,step=0.15,minSize=minSize,minSizeNG=minSizeNG)
ro3=loopQ3(map,disp=0,step=0.15,minSize=minSize,minSizeNG=minSizeNG)
ro4=loopQ4(map,disp=0,step=0.15,minSize=minSize,minSizeNG=minSizeNG)
# study results, first plot criteria
best=figCritN(m1=ro1,m2=ro2,m3=ro3,m4=ro4,NEW=TRUE,ONE=TRUE,title="Yield data",pdf=NULL)
# best probability vectors for a number of labels between 2 and 5
m1=best[1]
m2=best[2:3]
m3=best[4:6]
m4=best[7:10]
# build best zonings for a given number of labels (between 2 and 5), that implies calculating corrections for the best zonings determined in the exploration loop
# assign corresponding objects Z1, Z2, Z3, Z4 and values val1, val2, val3, val4
for (k in 1:4)
    {
	mk=get(paste("m",k,sep=""))
	critk=correctionTree(mk,map,minSize=minSize,minSizeNG=minSizeNG,disp=0,SAVE=T)
	res=searchNODcrit1(mk,critk)
	jj=res$ind[[1]][1]
	zk=critk$zk
	K=zk[[length(zk)]][[jj]]
	# order zones by increasing average zone value
	valk=valZ(map,K)$val
	ordk=valZ(map,K)$ord
	Zk=K$zonePolygone
	ii=0
	for (iZ in ordk)
    	    {
		ii=ii+1
    		Zk=setId(Zk,iZ,ii)
    	     }
	Zkname=paste("Z",k,sep="")
	assign(Zkname,Zk)
	valkname=paste("val",k,sep="")
	assign(valkname,valk)
    }

# for 4 labels, display data, best zonings and distribution of values within zones (boxplot)
   palCol=colorRampPalette(c("brown","yellow"))
   dispZ(map$step,map$krigGrid,zonePolygone=Z3,id=TRUE,palCol=palCol(length(Z3)))
   title("Best Zoning for nL=4")
   boxplot(val3,col=palCol(length(val3)))
    title("Distribution of values within zones")

# Session informations
```{r session,echo=FALSE,message=FALSE, warning=FALSE}
  sessionInfo()
```
